Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-07 report/report.tex
Add a note on why 2*positional accuracy was chosen as max distance for the collision study

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct) and ArcGIS (***).

@@

% TODO: Write disposition for implementation of the collision checker
In this implementation, roads of different types were allowed to merge into one another to form common intersections. To facilitate this, it was neccessary to work with a path-by-path representation of the point data. When two path share a node with common coordinates, they form an intersection which can be of multiple different types.

>>>>

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct) and ArcGIS (***) %TODO.

@@

% TODO: Write disposition for implementation of the collision checker
The maximum distance between two features was set to 2 times the positional accuracy, since then there will always be ample room to make changes to any features that would collide with the newly noved nodes, and thus we do not need to worry about feature collisions propagating.

In this implementation, roads of different types were allowed to merge into one another to form common intersections. To facilitate this, it was neccessary to work with a path-by-path representation of the point data. When two path share a node with common coordinates, they form an intersection which can be of multiple different types.
